003_ftx_mining.Rmd

### 2020-06-14 analysis/002_cr_els_matching.Rmd
no delay info from crossref. instead, the open archive info from elsevier is used

A few records have a date formats without day, which is used for the delayed calculation. We should therefore allow for a delay of up to  30 days.

```{r}
els_license_delay %>%
  filter(delay_in_days < 31) 
```

@@

```{sql, connection=con, output.var="els_hybrid_articles"}
SELECT *
FROM `api-project-764811344545.cr_dump_march_20.els_hybrid_cr`, unnest(license) as license
WHERE (REGEXP_CONTAINS(license.URL, 'creativecommons') AND license.content_version = 'vor') AND 
  (issued_year BETWEEN 2015 and 2019) AND
  license.delay_in_days < 31
```

Backup

```{r}
require(jsonlite)
jsonlite::stream_out(els_hybrid_articles, file(here::here("data", "els_hybrid_articles.json")))
```

>>>>

A few records have a date formats without day, which is used for the delayed calculation. We should therefore allow for a delay of up to  30 days. 
```{r}
els_license_delay %>%
  filter(delay_in_days < 31) 
```

But it seems that also some articles misses months. I will therefore obtain all cc tagged articles and validate immediate oa provision via the open archive tag

@@

```{sql, connection=con, output.var="els_hybrid_articles"}
SELECT *
FROM `api-project-764811344545.cr_dump_march_20.els_hybrid_cr`, unnest(license) as license
WHERE (REGEXP_CONTAINS(license.URL, 'creativecommons') AND license.content_version = 'vor') AND 
  (issued_year BETWEEN 2015 and 2019) 
```

Dataset with TDM Links

```{r}
els_tdm <- els_hybrid_articles %>%
  select(doi, link) %>%
  unnest(link) %>%
  filter(content_type == "text/xml",
         intended_application == "text-mining",
         content_version == "vor")
write_csv(els_tdm, here::here("data", "els_tmd_links.csv"))
```

### 2020-06-14 analysis/003_cr_xml_fetch.Rmd
no delay info from crossref. instead, the open archive info from elsevier is used

```{r}
require(jsonlite)
require(tidyverse)
require(crminer)
require(xml2)
require(here)
```

@@

```{r}
els_hybrid <- jsonlite::stream_in(file(here::here("data", "els_hybrid_articles.json")))
```

get tdm links

```{r}
elsevier_tdm <- els_hybrid %>%
  select(doi, link) %>%
  unnest(link) %>%
  filter(content_type == "text/xml",
         intended_application == "text-mining",
         content_version == "vor")
```

Apply function on every XML full-text link

```{r}
tt <- purrr::map(sample(elsevier_tdm$URL, 10), .f = purrr::safely(elsevier_parse))
```

>>>>

```{r}
require(tidyverse)
require(crminer)
require(xml2)
require(here)
source(here::here("R", "parse_els_xml.R"))
```

@@

```{r}
els_hybrid <- readr::read_csv(here::here("data", "els_tmd_links.csv"))
```

```{r}
tt <- plyr::llply(sample(elsevier_tdm$URL, 10), .f = purrr::safely(elsevier_parse), .progress = "text")
```
